Modular Model-Checking of a Byzantine Fault-Tolerant Protocol

### 2017-03-01 paper/paper.tex
Add note comparing model-checking of Rushby's model vs. ours

As a point of comparison, Rushby presents an elegant high-level model of \OM{1}, also in SAL, but using BDD-based model-checking~\cite{Rushby:OM1}. For small values, the verification is much faster, likely due to making only one call to SAL. However, for six relays and two receivers, it takes 449~seconds and timeouts (at one hour) for seven relays and two receivers.

>>>>

As a point of comparison, Rushby presents an elegant high-level model of
\OM{1}, also in SAL~\cite{Rushby:OM1}. For small numbers of relays/receivers,
the verification of Rushby's model is much faster, likely due to making only
one call to SAL. However, for six relays and two receivers, it takes
449~seconds and timeouts (at one hour) for seven relays and two receivers.
Checking Rushby's model requires use of symbolic, BDD-based model-checking
techniques which are well-known to scale poorly. On the other hand, our model
requires the use of $k$-induction which scales well, but requires (inductive)
invariants to be provided.
